Spatial Analysis

### 2021-05-03 Scripts/spatial_analisis.Rmd
exploring buffer

us_map <- st_as_sf(map("state", plot = FALSE, fill = TRUE))

@@

# Load it!
World_eez_sf <- st_read(dsn = path_world,
                        layer =file_path_sans_ext(fnam_world)) %>% 
  rename(eez_name = Name) %>% 
  st_transform(crs = 4326) %>% # 4326
  # st_transform(crs = "+proj=eck4") %>% # for tbular plot
  st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>% 
  filter(eez_name == "USA (East Coast)")

>>>>

States <- c("maine", "new hampshire", "massachusets", "connecticut", "rhode island", "new york", "new jersey", "delaware", "maryland", "virginia", "north carolina")

# US State Map (land)

land_sf <- st_as_sf(map("state", plot = FALSE, fill = TRUE)) %>% 
  filter(ID %in% States)

# ggplot(us_map) +
  # geom_sf()

# US EEZ map

@@

# Load it!
eez_sf <- st_read(dsn = path_world,
                        layer =file_path_sans_ext(fnam_world)) %>% 
  rename(eez_name = Name) %>% 
  st_transform(crs = 4326) %>% # 4326
  # st_transform(crs = "+proj=eck4") %>% # for tbular plot
  st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>% 
  filter(eez_name == "USA (East Coast)")

# ggplot(World_eez_sf) +
  # geom_sf()

# ggplot() +
#   geom_sf(data = World_eez_sf, aes(), color = "red") +
#   geom_sf(data = us_map, aes(), color = "blue")

# US state waters
# https://catalog.data.gov/dataset/federal-and-state-waters

# us_state_w <- rgdal::readOGR(dsn = "~/Downloads/FederalAndStateWaters/FederalAndStateWaters.gdb")
state_sf <-  st_read("~/Downloads/FederalAndStateWaters/FederalAndStateWaters.gdb") %>% 
  janitor::clean_names() %>% 
  mutate(jurisdicti = str_to_lower(jurisdicti)) %>% 
  filter(jurisdicti %in% States)

# plot <- state_sf %>%
  # st_simplify(preserveTopology = TRUE, dTolerance = 10000) %>%
  # ggplot()  +
  # geom_sf(aes(col = Jurisdicti))

# ggsave("plot.png",plot)

### Exploring spatial regions (a.k.a  buffers)

```{r}

## Test with st_buffer

test <- state_sf %>% 
  filter(jurisdicti == "maine") %>% 
  select(jurisdicti,Shape)

ggplot(test) +
  geom_sf()

pbuf = st_buffer(test, 100)

p <- ggplot() +
  geom_sf(data = test, aes(), color = "blue") +
  geom_sf(data = pbuf, aes(), color = "red")

ggsave("testplot.png",p)

### Test with library(ggforce)
# install.packages("ggforce")
library(ggforce)

 test <- state_sf %>% 
  filter(jurisdicti == "maine") %>% 
  select(jurisdicti,Shape)
